### 2015-12-14 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
exemplification and encoding are now primitive

\ de{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dio{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ da{\isacharcolon}{\isacharcolon}{\isacharprime}a%

@@

The Principia Metaphysica distinguishes between encoding and exemplifying, ... say more ...

  Encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is noted here as \isa{{\isasymlbrace}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymrbrace}}. 
  Encoding yields formulas and never propositional formulas. In the embedding encoding 
  is identified with predicate application.%

@@

\ \ \ \ {\isacharparenleft}T{\isacharparenleft}y{\isacharparenright}{\isacharcomma}T{\isacharparenleft}Q{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%

@@

  Exemplification yields propositional formulas. In the embedding exemplification 
  is identified with predicate application, just as encoding.%

@@

\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
The Principia Metaphysica supports \isa{n}-ary exemplification constructions. For pragmatical 
  reasons we consider here the cases only for \isa{n{\isasymle}{\isadigit{3}}}.%

@@

\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline

@@

\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{3}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}\ y{\isadigit{3}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%

@@

@@

  For pragmatical reasons we restrict ourselves here to the cases where $n\leq 3$. Binder notation is

@@

  achieved also for \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} ... need to find out.).%

@@

Question: What are the next two lemmata expected to return? So far they return truth. If that should
  be disabled (I guess that should then happen in the definition of implication), then we might run 
  into a problem with the definition of \isa{x\ \isactrlbold {\isacharequal}\isactrlsub E\ y} below. Discuss.%

@@

@@

>>>>

\ de{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dio{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ deio{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ da{\isacharcolon}{\isacharcolon}{\isacharprime}a%

@@

The Principia Metaphysica distinguishes between encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} and 
  exemplifying  \isa{{\isasymPi}\isactrlsup n{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isachardot}{\isachardot}{\isacharcomma}{\isasymkappa}\isactrlsub n}. ... say more ...
  Exemplification is supported here only for  \isa{{\isadigit{1}}{\isasymle}n{\isasymle}{\isadigit{3}}}.

  First we introduce the following primitive constants. These basic primitives are employed 
  below in the definition of our type-raised (to \isa{{\isacharprime}a\ opt}-types) operations  
  \isa{{\isasymlbrace}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymrbrace}} (for encoding) and  \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymrparr}}, \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{2}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isasymrparr}} and \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{3}}{\isasymrparr}}
  (for exemplification).%
\ enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}{\isasymRightarrow}io{\isachardoublequoteclose}\isanewline
\ exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\isanewline
\ exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ \isanewline
\ exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}%
Encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is noted below as \isa{{\isasymlbrace}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymrbrace}}.
  Encoding yields formulas and never propositional formulas.%

@@

\ \ \ \ {\isacharparenleft}T{\isacharparenleft}y{\isacharparenright}{\isacharcomma}T{\isacharparenleft}Q{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}enc\ y\ Q{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%

@@

  Exemplification yields propositional formulas.%

@@

\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}exe{\isadigit{1}}\ Q\ y{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
The Principia Metaphysica supports \isa{n}-ary exemplification constructions. 
  We support the cases for \isa{{\isadigit{1}}{\isasymle}n{\isasymle}{\isadigit{3}}}.%

@@

\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}exe{\isadigit{2}}\ Q\ y{\isadigit{1}}\ y{\isadigit{2}}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline

@@

\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{3}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}exe{\isadigit{3}}\ Q\ y{\isadigit{1}}\ y{\isadigit{2}}\ y{\isadigit{3}}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%

@@

\ binderTest{\isacharcolon}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\ x{\isacharparenright}\ {\isacharequal}\ \isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymphi}\ x{\isacharparenright}{\isachardoublequoteclose}%
\isacommand{by}\isamarkupfalse%

@@

  Similar to before, we support only the cases where $n\leq 3$. Binder notation is

@@

  achieved also for \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}} ... need to find out.).%

@@

The next two statements are not theorems; Nitpick reports countermodels%

@@

However, the next two statements are of course valid.%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%

@@

\isamarkupsubsection{Negation of Properties%
\ notProp{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymsim}{\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{5}}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{5}}{\isadigit{9}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymsim}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isasymPhi}\ of\ \isanewline
\ \ \ \ T{\isacharparenleft}{\isasymPsi}{\isacharparenright}\ {\isasymRightarrow}\ \isactrlbold {\isasymlambda}x{\isachardot}\isactrlbold {\isasymnot}{\isasymlparr}{\isasymPhi}{\isacharcomma}x\isactrlsup T{\isasymrparr}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}deio{\isacharparenright}{\isachardoublequoteclose}%
\isamarkupsubsection{Individual Constant \isa{\isactrlbold a\isactrlsub V} and Function Term \isa{\isactrlbold a\isactrlsub G}%
\ a{\isacharunderscore}V{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold a\isactrlsub V{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold a\isactrlsub V\ {\isasymequiv}\ \isactrlbold {\isasymiota}x{\isachardot}\ {\isacharparenleft}{\isasymlparr}A{\isacharbang}{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}F\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ F\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ a{\isacharunderscore}G{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold a\isactrlsub {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{5}}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{5}}{\isadigit{9}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold a\isactrlsub G\ {\isasymequiv}\ \isactrlbold {\isasymiota}x{\isachardot}\ {\isacharparenleft}{\isasymlparr}A{\isacharbang}{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}F\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ G{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
